The language of generalization: Probability, vagueness, and interaction

### 2018-10-01 paper/case2-habituals.Rmd
clean up figures, table of exampels

figure.habituals.priors.scatter <- ggplot(
  rs.habituals.bda.posterior.predictive.measurementSpace.wide %>%
                    filter(item %in% example.habituals, gender == "female"),
       aes(x = `% people who have done action before`, 
           y = `Frequency of doing action (log scale)`, 
           color = gender, label = item))+
  scale_color_solarized()+
  geom_point(data = rs.habituals.bda.posterior.predictive.measurementSpace.wide %>%
                    filter(!(item %in% example.habituals) | gender == "male"),
             inherit.aes = F, 
             aes(
               x = `% people who have done action before`, 
               y = `Frequency of doing action (log scale)`, color = gender))+
  geom_point()+
  geom_label_repel(segment.alpha = 1,label.size = 0.25,
                   force = 10, size = 2, color = 'black')+

  #geom_errorbar(alpha = 0.3)+geom_errorbarh(alpha = 0.3)+
  coord_fixed(1/7.5)+
  #xlab("Model posterior predictive")+
  #ylab("Empirical means")+
  theme(legend.position = c(0.83, 0.16))+
  scale_y_continuous(
      limits = c(-1.5, 6),
      breaks = c(0, 2.5, 4, 5.9),
      labels = c( "annually", "monthly", "weekly", "daily")
    )+
  scale_x_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))

@@

```{r habituals-prior-figure, fig.width = 15,fig.asp = 0.37, out.width = "\\textwidth", fig.pos = "!h", fig.cap="Prevalence priors for events (Expt. 2a). A: Parameters of prevalence priors for the 31 items in Expt. 2. Items cover much of the range of possible parameter values. B: Reconstructed prevalence priors. In order to show frequencies for events that are very rare across people (e.g., \"writes novels\"), extremely low frequencies (\\emph{almost never}) are omitted. Instead, height of the bars on left denote the Maximum A-Posteriori values of the mixture component (in terms of \\emph{proportion of people who have never done action before}), reflecting the (inverse) popularity of the event across people.", cache = F}
cowplot::plot_grid(
  figure.habituals.priors.scatter + theme(plot.margin = unit(c(6,6,6,0), "pt")), 
  figure.habituals.priors.marginals + theme(plot.margin = unit(c(6,0,6,6), "pt")),
  labels = c("A", "B"), #nrow = 1,
  align = 'h',
  rel_widths = c(1, 3)
  )
```

@@

```{r habituals-endorsement-bars, fig.width = 8}
habituals.endorsement.bars <- ggplot(md.hab.long %>%
                                       mutate(src = factor(src, levels = c(
                                          "Referent frequency",
                                         "Distinctiveness +\n referent frequency", 
                                         "Fixed semantics",
                                        "Uncertain semantics", "Human data"
                                       )),
                                       habitual = factor(habitual, levels = c( 
                       "climbs mountains","hikes", "runs",
                      "smokes cigarettes","drinks coffee",
                      "goes to the movies", "watches space launches",
                       "writes poems", "writes novels"
                       ))), aes ( y = prediction, ymin = prediction_lower, ymax = prediction_upper,
                  x = src, fill = logAnnualRate, group = logAnnualRate))+
  #geom_abline(intercept = 0, slope = 1, lty = 3)+
  #geom_linerange(alpha = 0.15)+
  geom_col(position = position_dodge(), color = 'black'
           #width = 0.7
           )+
  geom_errorbar(alpha = 0.7,
                position = position_dodge())+
  #geom_point(shape = 21, size = 3)+
  #scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
  scale_fill_viridis(
      breaks = c(-0.5, 1.1, 3.5, 5),
      labels = c("5 years", "year", "month", "week")
  )+
  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
  #coord_fixed()+
  ylab("Habitual endorsement")+
  xlab("")+
  #facet_grid(src~habitual, scales = 'free')+
  facet_wrap(~habitual)+
  guides(fill = F)+#guide_colorbar(ticks = F, title = "Time interval"))+
  theme(strip.text.y = element_text(hjust = 0, angle = 0),#, vjust = 1),
        axis.text.x = element_text(vjust = 1, hjust = 1, angle = 45),
        legend.position = "right")

@@

```{r habitual-endorsment-scatters}
habituals.endorsement.models <- md.hab %>% mutate(src = factor(src, levels = c(
                                      "regression_freq", 
                                      "habituals_model",
                                      "regression_freq_distinct",
                                      "some_model"
                                     ),
                      labels = c(
                                 "Referent frequency", 
                                 "Endorsement model",
                                 "Distinctiveness + \n referent frequency",
                                 "Lesioned model\n(no vagueness)"
                                 ) )) %>%
ggplot(., aes ( x = prediction, xmin = prediction_lower, xmax = prediction_upper,
                  y = MAP_h, ymin = low, ymax = high, fill = logAnnualRate))+
  geom_abline(intercept = 0, slope = 1, lty = 3)+
  geom_linerange(alpha = 0.15)+
  geom_errorbarh(alpha = 0.15)+
  geom_point(shape = 21, size = 3)+
  scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
  scale_fill_viridis(
      breaks = c(-0.5, 1.1, 3.5, 5),
      labels = c("5 years", "year", "month", "week")
  )+  coord_fixed()+
  xlab("Model prediction")+
  ylab("Human endorsement")+
  facet_wrap(~src, ncol = 2, strip.position = "top")+
  guides(fill = guide_colorbar(ticks = F, title = "Time interval"))+
  theme(strip.text.y = element_blank(),# element_text(angle = 0, hjust= 0),
        #legend.direction = 'horizontal',
        #legend.position = c(0.025,0.975),
        legend.position ='bottom',
        legend.text = element_text(angle = 45)
        #legend.justification = c(1,1)
        )
```

```{r habituals-model-insets, fig.width = 8, cache = T}
habituals.endorsement.insets <- hab.listener.predictions %>% 
    mutate(Parameter = factor(Parameter, levels = c("state_Prior",
                                                  "state_Posterior"
                                                  ),
                            labels = c("Prevalence Prior",
                                       "Posterior given Habitual")),
         action = factor(action, levels = c( 
                       "climbs mountains","hikes", "runs",
                      "smokes cigarettes","drinks coffee",
                      "goes to the movies", "watches space launches",
                       "writes poems", "writes novels"
                       ))
                                #"climbs mountains", "hikes", "runs",
                              #"goes to the movies", "smokes cigarettes"
                              ) %>%
  ggplot(., aes( x = value, fill = Parameter, color = Parameter, lty = Parameter, alpha = Parameter ))+
  geom_density(aes(y = ..scaled..), adjust = 1, size = 1)+
  facet_wrap(~action, nrow = 2)+
  # geom_text_repel(data = category.text.labels,
  #                 aes(label = category, x = x , y = y),
  #                 inherit.aes = F, color = "#2b83ba")+
  #scale_fill_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
  #scale_color_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
  scale_fill_manual(values = c("#636363", "#d7191c"))+#, "#2b83ba"))+
  scale_color_manual(values = c("#636363", "#d7191c"))+#, "#2b83ba"))+
  scale_alpha_manual(values = c(0.6, 0.4))+#, 0))+
  #scale_linetype_manual(values = c(3, 4, 2, 1))+
  #scale_linetype_manual(values = c(3, 4, 1))+
  #scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
  scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
  xlab("Frequency (log scale)") +
  ylab("Scaled probability density")+
  theme(legend.position = c(0.9, 0), 
        legend.title = element_blank(),
        axis.text.x = element_text(angle = 90, vjust = 1))+
        #axis.title.y = element_text(hjust = 1))+
  scale_x_continuous(limits = c(-5, 8), 
                     breaks = c(-5, 0, 2.5, 4, 5.9),
                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))
```

```{r habituals-endorsement-figure, fig.width = 13, fig.asp=0.7, fig.cap="Endorsing generalizations about events. A: Endorsements for nine events given different frequencies of action by human participants and four models. B: Human elicited endorsements for ninety-three habitual sentences as a function of the referent (log) frequency of action. Top right: Model fits for all ninety-three habitual sentences by each model. C: Nine example frequency priors and posteriors upon hearing the generalization. These distributions are inferred using both data sources from Expts. 2a and 2b.", out.width = "\\textwidth", fig.pos = "!h", cache = F}

#hab.legend <- get_legend(habituals.endorsement.models)
fig.hab.endorse.bars <- habituals.endorsement.bars +
  theme(plot.margin = unit(c(6,6,6,6), "pt")) #+ ggtitle("prevalence priors")
fig.hab.endorse.scatters <- habituals.endorsement.models +
  theme(plot.margin = unit(c(6,6,6,6), "pt")) # + theme(legend.position="none") #+ ylab("")
fig.hab.endorse.priors <- habituals.endorsement.insets +
  theme(plot.margin = unit(c(16,36,16,36), "pt"))

plot_grid(
    plot_grid(fig.hab.endorse.bars, fig.hab.endorse.scatters, nrow = 1, labels = c("A", "B"),
              rel_widths = c(2, 1)),
            fig.hab.endorse.priors,
                            labels = c("", "C"), nrow = 2,
                            #axis = 'lr', 
                        #align = 'v', 
                            rel_heights = c(1.7, 1))

@@

```{r habituals-predictive-rsa, cache = T, eval=T}
n_chains <- 3
# n_samples <- 500000
# burn <- n_samples / 2
# lg <- 150
model_prefix <- "results-habituals-predictive-jointModel-S1-smtncs_habitual-"
model_prefix <- "results-habituals-predictive-meanPredictive-min-5-jointModel-S1-smtncs_habitual-"
n_samples <- 100000
burn <- n_samples / 2
lg <- 50

@@

```{r habituals-predictive-endorsement-scatters, cache = F}
habituals.endorsement.pred.scatters <- m.hab.predictive.endorse.allModels %>%
  mutate(condition = factor(condition, levels = c("preventative", "baseline", "enabling")),
         src =factor(src , levels = c("human data", "regression_pastfreq",
                                     "past_model", "regression_futurefreq",
                                      "predictive_model"),
                     labels= c("Human data","regression_pastfreq", 
                                "Uncertain semantics\n(Past)", "Linear model\n(Predictive frequency)","Uncertain semantics\n(Predictive)"))) %>%
  filter(!(src %in% c("Human data", "regression_pastfreq"))) %>%
ggplot(., 
       aes (x = MAP, xmin = cred_lower, xmax = cred_upper, 
            y = MAP_h, ymin= low, ymax = high, fill = condition,
            shape = condition))+
  geom_abline(intercept = 0, slope = 1, lty = 3)+
  #geom_linerange(alpha = 0.15)+
  #geom_col(position = position_dodge(0.7), color = 'black', width = 0.7)+
  geom_linerange(alpha = 0.7, size = 1)+
  geom_errorbarh()+
  geom_point(size = 3)+
  scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
  scale_shape_manual(values=c(21,22,23))+
  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
  scale_fill_brewer(type = "seq", palette = 2)+
  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
  coord_fixed()+
  ylab("Habitual endorsement")+
  xlab("Model prediction")+
  facet_grid(.~src)+
  theme(legend.position = "right")
```

```{r habituals-predictive-figure, fig.cap="A: Example empirical and predicted endorsements for habituals in three conditions. B: Predicted frequency as a function of past frequency and condition manipulation (enabling, preventative, and baseline). C: Model fits for the uncertain threshold model using past frequency, linear model based on future frequency, and uncertain threshold model using future frequency.", fig.width = 12,  fig.asp = 0.7,out.width = "\\textwidth", fig.pos = "!h", cache=F}
plot_grid(
  habituals.endorsement.pred.bars +
    theme(plot.margin = unit(c(6,6,6,6), "pt"), legend.position="none",
          axis.title.x = element_blank()),
  plot_grid(
    fig.hab.freq.predictive.vs.past + 
     theme(plot.margin = unit(c(0,6,0,0), "pt"), legend.position="none",
           axis.text = element_text(size = 8),
           axis.title = element_text(size = 9)),
    habituals.endorsement.pred.scatters +
      theme(plot.margin = unit(c(0,0,12,12), "pt")),
    labels = c("B", "C"),
    nrow = 1,  axis = 'tblr', rel_widths = c(1, 2.3)), 
  labels = c("A", ""), 
  nrow = 2, align = 'v', axis = 'lr', rel_heights = c(3.1, 2))
```

>>>>

figure.habituals.priors.scatter <- ggplot(
  rs.habituals.bda.posterior.predictive.measurementSpace.wide %>%
                    filter(item %in% example.habituals, gender == "female"),
       aes(x = `% people who have done action before`, 
           y = `Frequency of doing action (log scale)`, 
           color = gender, label = item))+
  scale_color_solarized()+
  geom_point(data = rs.habituals.bda.posterior.predictive.measurementSpace.wide %>%
                    filter(!(item %in% example.habituals) | gender == "male"),
             inherit.aes = F, 
             aes(
               x = `% people who have done action before`, 
               y = `Frequency of doing action (log scale)`, color = gender))+
  geom_point()+
  geom_label_repel(segment.alpha = 1,label.size = 0.25,
                   force = 10, size = 4, color = 'black')+

  #geom_errorbar(alpha = 0.3)+geom_errorbarh(alpha = 0.3)+
  coord_fixed(1/7.5)+
  #xlab("Model posterior predictive")+
  #ylab("Empirical means")+
  theme(legend.position = c(0.83, 0.16),
        legend.text=element_text(size=16))+
  scale_y_continuous(
      limits = c(-1.5, 6),
      breaks = c(0, 2.5, 4, 5.9),
      labels = c( "annually", "monthly", "weekly", "daily")
    )+
  scale_x_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))

@@

```{r habituals-prior-figure, fig.width = 15,fig.asp = 0.7, out.width = "\\textwidth", fig.pos = "!h", fig.cap="Prevalence priors for events (Expt. 2a). A: Parameters of prevalence priors for the 31 items in Expt. 2. Items cover much of the range of possible parameter values. B: Reconstructed prevalence priors. In order to show frequencies for events that are very rare across people (e.g., \"writes novels\"), extremely low frequencies (\\emph{almost never}) are omitted. Instead, height of the bars on left denote the Maximum A-Posteriori values of the mixture component (in terms of \\emph{proportion of people who have never done action before}), reflecting the (inverse) popularity of the event across people.", cache=F}
plot_grid(
  figure.habituals.priors.scatter + theme(plot.margin = unit(c(6,6,6,0), "pt")), 
  figure.habituals.priors.marginals + theme(plot.margin = unit(c(6,0,6,6), "pt")),
  labels = c("A", "B"), nrow = 2,
  align = 'h',
  rel_heights = c(1, 1)
  )
```

@@

```{r habituals-endorsement-bars, fig.width = 8,cache=F}
habituals.endorsement.bars <- ggplot(md.hab.long %>%
                                       mutate(src = factor(src, levels = c(
                                          "Referent frequency",
                                         "Distinctiveness +\n referent frequency", 
                                         "Fixed semantics",
                                        "Uncertain semantics", "Human data"
                                       )),
                                       habitual = factor(habitual, levels = c( 
                       "climbs mountains","hikes", "runs",
                      "smokes cigarettes","drinks coffee",
                      "goes to the movies", "watches space launches",
                       "writes poems", "writes novels"
                       ))), aes ( y = prediction, ymin = prediction_lower, ymax = prediction_upper,
                  x = src, fill = logAnnualRate, group = logAnnualRate))+
  #geom_abline(intercept = 0, slope = 1, lty = 3)+
  #geom_linerange(alpha = 0.15)+
  geom_col(position = position_dodge(), color = 'black'
           #width = 0.7
           )+
  geom_errorbar(alpha = 0.7,
                position = position_dodge())+
  #geom_point(shape = 21, size = 3)+
  #scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
  scale_fill_viridis(
      breaks = c(-0.5, 1.1, 3.5, 5),
      labels = c("5 years", "year", "month", "week")
  )+
  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
  #coord_fixed()+
  ylab("Habitual endorsement")+
  xlab("")+
  #facet_grid(src~habitual, scales = 'free')+
  facet_wrap(~habitual)+
  guides(fill = F)+#guide_colorbar(ticks = F, title = "Time interval"))+
  theme(strip.text.y = element_text(hjust = 0, angle = 0),#, vjust = 1),
        axis.text.x = element_text(vjust = 1, hjust = 1, angle = 45, size = 10),
        legend.position = "right")

@@

```{r habitual-endorsment-scatters, cache=F}
habituals.endorsement.models <- md.hab %>% mutate(src = factor(src, levels = c(
                                      "regression_freq", 
                                      "habituals_model",
                                      "regression_freq_distinct",
                                      "some_model"
                                     ),
                      labels = c(
                                 "Referent frequency", 
                                 "Endorsement model",
                                 "Distinctiveness + \n referent frequency",
                                 "Lesioned model\n(no vagueness)"
                                 ) )) %>%
ggplot(., aes ( x = prediction, xmin = prediction_lower, xmax = prediction_upper,
                  y = MAP_h, ymin = low, ymax = high, fill = logAnnualRate))+
  geom_abline(intercept = 0, slope = 1, lty = 3)+
  geom_linerange(alpha = 0.15)+
  geom_errorbarh(alpha = 0.15)+
  geom_point(shape = 21, size = 3)+
  scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
  scale_fill_viridis(
      breaks = c(-0.5, 1.1, 3.5, 5),
      labels = c("5 years", "year", "month", "week")
  )+  coord_fixed()+
  xlab("Model prediction")+
  ylab("Human endorsement")+
  facet_wrap(~src, ncol = 2, strip.position = "top")+
  guides(fill = guide_colorbar(ticks = T, title = "Time interval"))+
  theme(strip.text.y = element_blank(),# element_text(angle = 0, hjust= 0),
        legend.direction = 'horizontal',
        #legend.position = c(0.025,0.975),
        legend.position ='bottom',
        legend.text = element_text(angle = 45, hjust = 0.5, vjust = 0.5)
        #legend.justification = c(1,1)
        )
```

```{r habituals-model-insets, fig.width = 8, cache=F}
habituals.endorsement.insets <- hab.listener.predictions %>% 
    mutate(Parameter = factor(Parameter, levels = c(                                                  "state_Posterior",
"state_Prior"
                                                  ),
                            labels = c(
                                       "Habitual Interpretation",
                                       "Prevalence Prior")),
         action = factor(action, levels = c( 
                       "climbs mountains","hikes", "runs",
                      "smokes cigarettes","drinks coffee",
                      "goes to the movies", "watches space launches",
                       "writes poems", "writes novels"
                       ))
                                #"climbs mountains", "hikes", "runs",
                              #"goes to the movies", "smokes cigarettes"
                              ) %>%
  ggplot(., aes( x = value, group = Parameter, y = Parameter ))+
  #geom_density(aes(y = ..scaled..), adjust = 1, size = 1)+
  ggridges::geom_density_ridges(scale = 1, alpha = 0.3, adjust = 1) +
  facet_wrap(~action, nrow = 1)+
  # geom_text_repel(data = category.text.labels,
  #                 aes(label = category, x = x , y = y),
  #                 inherit.aes = F, color = "#2b83ba")+
  #scale_fill_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
  #scale_color_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
  scale_fill_manual(values = c("#636363", "#d7191c"))+#, "#2b83ba"))+
  scale_color_manual(values = c("#636363", "#d7191c"))+#, "#2b83ba"))+
  scale_alpha_manual(values = c(0.6, 0.4))+#, 0))+
  #scale_linetype_manual(values = c(3, 4, 2, 1))+
  #scale_linetype_manual(values = c(3, 4, 1))+
  #scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
  #scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
  xlab("Frequency (log scale)") +
  ylab("")+
  theme(legend.position = c(0.9, 0), 
        legend.title = element_blank(),
        axis.text.x = element_text(angle = 90, vjust = 1),
        axis.title.y =  element_blank())+
        #axis.title.y = element_text(hjust = 1))+
  scale_x_continuous(limits = c(-5, 8), 
                     breaks = c(-5, 0, 2.5, 4, 5.9),
                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))
```

```{r habituals-endorsement-figure, fig.width = 16, fig.asp=0.65, fig.cap="Endorsing generalizations about events. A: Endorsements for nine events given different frequencies of action by human participants and four models. B: Human elicited endorsements for ninety-three habitual sentences as a function of the referent (log) frequency of action. Top right: Model fits for all ninety-three habitual sentences by each model. C: Nine example frequency priors and posteriors upon hearing the generalization. These distributions are inferred using both data sources from Expts. 2a and 2b.", out.width = "\\textwidth", fig.pos = "!h", cache=F}
#hab.legend <- get_legend(habituals.endorsement.models)
fig.hab.endorse.bars <- habituals.endorsement.bars +
  theme(plot.margin = unit(c(6,0,6,12), "pt")) #+ ggtitle("prevalence priors")
fig.hab.endorse.scatters <- habituals.endorsement.models +
  theme(plot.margin = unit(c(6,0,6,0), "pt")) # + theme(legend.position="none") #+ ylab("")
fig.hab.endorse.priors <- habituals.endorsement.insets +
  theme(plot.margin = unit(c(16,0,0,0), "pt"))

plot_grid(
    plot_grid(fig.hab.endorse.bars, fig.hab.endorse.scatters, nrow = 1,
              labels = c("A", "B"),
              rel_widths = c(2, 1)),
            fig.hab.endorse.priors,
                            labels = c("", "C"), nrow = 2,
                            #axis = 'lr',
                        #align = 'v',
                            rel_heights = c(1.6, 1))

@@

```{r habituals-predictive-rsa, eval=T}
n_chains <- 3
# n_samples <- 500000
# burn <- n_samples / 2
# lg <- 150
model_prefix <- "results-habituals-predictive-jointModel-S1-smtncs_habitual-"
model_prefix <- "results-habituals-predictive-meanPredictive-min-5-jointModel-S1-smtncs_habitual-"
n_samples <- 100000
burn <- n_samples / 2
lg <- 50

@@

```{r habituals-predictive-endorsement-scatters, cache = F}
habituals.endorsement.pred.scatters <- m.hab.predictive.endorse.allModels %>%
  mutate(condition = factor(condition, levels = c("preventative", "baseline", "enabling")),
         src =factor(src , levels = c("human data", "regression_pastfreq",
                                     "past_model", "regression_futurefreq",
                                      "predictive_model"),
                     labels= c("Human data","regression_pastfreq", 
                                "Uncertain semantics\n(Past frequency)", "Linear model\n(Predictive frequency)","Uncertain semantics\n(Predictive frequency)"))) %>%
  filter(!(src %in% c("Human data", "regression_pastfreq"))) %>%
ggplot(., 
       aes (x = MAP, xmin = cred_lower, xmax = cred_upper, 
            y = MAP_h, ymin= low, ymax = high, fill = condition,
            shape = condition))+
  geom_abline(intercept = 0, slope = 1, lty = 3)+
  #geom_linerange(alpha = 0.15)+
  #geom_col(position = position_dodge(0.7), color = 'black', width = 0.7)+
  geom_linerange(alpha = 0.7, size = 1)+
  geom_errorbarh()+
  geom_point(size = 3)+
  scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
  scale_shape_manual(values=c(21,22,23))+
  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
  scale_fill_brewer(type = "seq", palette = 2)+
  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
  coord_fixed()+
  ylab("Habitual endorsement")+
  xlab("Model prediction")+
  facet_grid(.~src)+
  theme(legend.position = "top")
```

```{r habituals-predictive-figure, fig.cap="A: Example empirical and predicted endorsements for habituals in three conditions. B: Predicted frequency as a function of past frequency and condition manipulation (enabling, preventative, and baseline). C: Model fits for the uncertain threshold model using past frequency, linear model based on future frequency, and uncertain threshold model using future frequency.", fig.width = 12,  fig.asp = 0.7, out.width = "\\textwidth", fig.pos = "!h", cache=F}
plot_grid(
   habituals.endorsement.pred.bars +
     theme(plot.margin = unit(c(6,6,6,6), "pt"), legend.position="none",
           axis.title.x = element_blank()),
   plot_grid(
     fig.hab.freq.predictive.vs.past +
      theme(plot.margin = unit(c(0,6,0,0), "pt"), legend.position="none",
            axis.text = element_text(size = 8),
            axis.title = element_text(size = 9)),
habituals.endorsement.pred.scatters +
       theme(plot.margin = unit(c(0,0,0,0), "pt")),
     labels = c("B", "C"),
     nrow = 1,  axis = 'tblr', rel_widths = c(1, 2.3)),
   labels = c("A", ""),
   nrow = 2, align = 'v', axis = 'lr', rel_heights = c(3.1, 2))
```

### 2018-10-01 paper/comgen-paper.Rmd
clean up figures, table of exampels

```{r global_options, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(fig.width=6, fig.height=5, fig.crop = F, fig.path='figs/',
                      echo=FALSE, warning=FALSE, cache=T, message=FALSE, sanitize = T)

```

```{r libraries, cache = F}
library(papaja)
library(formatR)
library(rwebppl)
library(xtable)
library(tidyverse)
library(forcats)
library(langcog)
library(coda)
library(ggthemes)
library(ggrepel)
library(jsonlite)
library(gridExtra)
library(lme4)
library(knitr)
library(kableExtra)
library(cowplot)
library(magick)
library(viridis)
theme_set(theme_few())
estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}
hdi_upper<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}
hdi_lower<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}
logmeanexp <- function(x){
  x.num <- as.numeric(x)
  xstar = max(x.num)
  return(xstar + log(mean(exp(x.num - xstar))))
}

@@

```{r workedExamples, results="asis"}
worked.examples <- data.frame(
  example = c("1. Dogs bark",
              "2. Kangaroos have spots",
              "3. Sharks don't eat people",
              "4. Robins lay eggs",
              "5. Robins are female",
              "6. Mosquitos carry malaria", 
              "7. Mary handles the mail from Antarcita",
              "8. Supreme Court Justices have even social security numbers",
              "9. Elephants live in Africa and Asia"),
  `referent prevalence` = c("95%", "5%", "85%", "50%", "50%", "5%", "0 times", "100%", "~50%/50%"),
  `intuitive truth value` = c(
    "T", "F", "F", "T", "U",
    "T", "T", "F", "T" 
  ),
  `potential issue` = c(
    "Not all dogs bark",
    "Some kangaroos could have spots",
    "Most sharks don't eat people",
    "Only female (50%) of robins lay eggs",
    "Roughly same number of robins that lay eggs are female",
    "Very few mosquitos actually carry malaria",
    "Hypothetically, there has never been any mail from Antarcita",
    "Even if 100% have even social security numbers",
    "Impossible for most to live in Africa and most to live in Asia"
  )
)

examples <- xtable::xtable(worked.examples, 
                       caption = "Example generalizations that a theory of generics should correctly predict.", 
                       align=c('p{1.5in}', 'p{1.2in}| ',' |p{1in}|','p{1in}|','p{2in} |'))

@@

print(examples, 
      type="latex", 
      comment = F,
       #table.placement = "h", 
      tabular.environment = "longtable",
      hline.after=-1:nrow(examples),
      size="\\fontsize{9pt}{10pt}\\selectfont", 
      include.rownames=FALSE,
      sanitize.colnames.function = bold
      #add.to.row = addtorow
      )
```

>>>>

```{r global_options, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(fig.width=6, fig.height=5, fig.crop = F, fig.path='figs/',
                      echo=FALSE, warning=FALSE, cache=T, message=FALSE, sanitize = T)
```

```{r libraries, cache=F}
library(papaja)
library(formatR)
library(rwebppl)
library(xtable)
library(tidyverse)
library(forcats)
library(langcog)
library(coda)
library(ggthemes)
library(ggrepel)
library(jsonlite)
library(gridExtra)
library(lme4)
library(knitr)
library(kableExtra)
library(cowplot)
library(magick)
library(viridis)
theme_set(theme_few())
estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}
hdi_upper<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}
hdi_lower<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}
logmeanexp <- function(x){
  x.num <- as.numeric(x)
  xstar = max(x.num)
  return(xstar + log(mean(exp(x.num - xstar))))
}

@@

```{r workedExamples, results="asis"}
worked.examples <- data.frame(
  Example = c("1. Dogs bark",
              "2. Kangaroos have spots",
              "3. Sharks don't eat people",
              "4. Robins lay eggs",
              "5. Robins are female",
              "6. Mosquitos carry malaria", 
              "7. Mary handles the mail from Antarcita",
              "8. Supreme Court Justices have even social security numbers",
              "9. Elephants live in Africa and Asia"),
  `referent prevalence` = c("95%", "5%", "85%", "50%", "50%", "5%", "0 times", "100%", "50%/50%"),
  `intuitive truth value` = c(
    "T", "F", "F", "T", "U",
    "T", "T", "F", "T" 
  ),
  `potential issue` = c(
    "Not all dogs bark",
    "Some kangaroos could have spots",
    "Most sharks don't eat people",
    "True, even though only female robins (50%) lay eggs",
    "Not true, but same number that lay eggs (50%)",
    "Very few mosquitos actually carry malaria",
    "True even if there has never been any mail from Antarcita",
    "False even if 100% have even social security numbers",
    "Impossible for most to live in Africa and most to live in Asia"
  )
) %>%
  rename("Referent prevalence" = referent.prevalence,
         "Intuitive truth value" = intuitive.truth.value,
         "Issue" = potential.issue)

worked.examples.tab <- xtable::xtable(worked.examples, 
                       caption = "Example generalizations that a theory of generics should correctly predict.", 
                       align=c('p{1.5in}', 'p{2in}| ',' |p{1.25in}|','p{0.75in}|','p{2in} |'))

@@

print(worked.examples.tab, 
      type="latex", 
      comment = F,
       #table.placement = "h", 
      #tabular.environment = "longtable",
      hline.after=-1:nrow(worked.examples.tab),
      size="\\fontsize{9pt}{10pt}\\selectfont", 
      include.rownames=FALSE,
      sanitize.colnames.function = bold
      #add.to.row = addtorow
      )
```
